Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2016-11-23 WSSSPE4_report/wg_open_research_index.tex
finishing first draft of open research index working group section

\note{Dan to write this}

@@

The members of this group at WSSSPE4 were:
Gabrielle Allen,
Bruce Childers,
Robert Haines,
Caroline Jay,
Dan Katz,
Daniel Mosse,
Kyle Niemeyer,
and
Robert McDonald.

@@

Alternatively or additionally, we could build a mailing list for us and discuss further, depending on how receptive others are to this idea.  At WSSSPE4, there seemed to be enough interest to do this, so we set up a Slack channel within the WSSSPE team, called \#wg-open-research-idx.  (See \S\ref{sec:slack} to join the Slack WSSSPE team.)

\paragraph{Possible Plans}

Look at curriculum lattes (Brazil) and/or Researchfish (UK).  It has some problems that people don?t like, could check what features it has and what the issues are

Look at what CrossRef data is

What research products should we track?

What model should be used?
- Crawling and obtaining data
- Consortium model
- Need analysis and decision

Need agreements with publishers, repositories, services
- Some of these will have costs, though some may be free
- Need to determine costs
- Perhaps publishers would pay us to be listed eventually, as we gain power
- To some extent, we would be competing with some of the publishers? products

If crawling model:
- How to crawl all of these products?
- What data (metadata) should be the output of the crawls?
    - What happens when the products being crawled and/or their metadata change?
- How to store all of this data (metadata)?

What services to provide on this data (metadata)?

Who will create these services?

What services will the publishers allow to be provided?

Need to develop a plan that shows incremental progress and successes

Consider applying to Google project call to get Google interest and support?

@@

The working group discussed a number of SMART steps, though most of them did not fulfill all the SMART criteria:

@@

Find a PI (we suggest Neil Chue Hong)

Apply for initial funding
- For the US, consider Arnold Foundation Open Science award as a planning activity (who, due Dec 15)
- For the UK, ?

Determine project name, initial vision, initial mission, logo (who, when)

Identify initial use cases (who, when)

Identify potential stakeholders and partners (who, when)

Discuss this idea with potential partners (who, when)
- Get their feedback \& buy-in
- While doing so, seek suggestions for the right project manager to coordinate this

Build up an advisory board (who, when)

Build up a leadership committee and determine a leader (who, when)

Hire a project manager (who, when)

Iterate use case with stakeholders (who, when)
- E.g. funders, Researchfish, researchers, ?

Iterate vision \& mission with leadership committee and advisory board (who, when)

Develop initial development plan (who, when)

@@

If you are interested in more information, please join the WSSSPE team's Slack channel for this working group: \#wg-open-research-idx.  (See \S\ref{sec:slack} to join the Slack WSSSPE team.)

>>>>

%\note{Dan to write this}

@@

The members of this group at WSSSPE4 were:
Gabrielle Allen,
Bruce Childers,
Robert Haines,
Caroline Jay,
Dan Katz,
Robert McDonald,
Daniel Mosse,
and 
Kyle Niemeyer.

@@

Alternatively or additionally, we could build a mailing list for us and discuss further, depending on how receptive others are to this idea.  At WSSSPE4, there seemed to be enough interest to do this, so we set up a Slack channel within the WSSSPE team, called \#wg-open-research-idx.  (See \S\ref{sec:slack} for instructions on how to join the Slack WSSSPE team.)

We also discussed some possible more detailed plans:

\begin{enumerate}
\item Look at curriculum lattes (Brazil) and/or Researchfish (UK).  They have some problems that people don't like, we could check what features they has and what the issues are.

\item Look at what CrossRef data is

\item What research products should we track?

\item What model should be used?
- Crawling and obtaining data
- Consortium model
- Need analysis and decision

\item Need agreements with publishers, repositories, services
- Some of these will have costs, though some may be free
- Need to determine costs
- Perhaps publishers would pay us to be listed eventually, as we gain power
- To some extent, we would be competing with some of the publishers? products

\item If crawling model:
- How to crawl all of these products?
- What data (metadata) should be the output of the crawls?
    - What happens when the products being crawled and/or their metadata change?
- How to store all of this data (metadata)?

\item What services to provide on this data (metadata)?

\item Who will create these services?

\item What services will the publishers allow to be provided?

\item Need to develop a plan that shows incremental progress and successes

\item Consider applying to Google project call to get Google interest and support?
\end{enumerate}

@@

The working group discussed a number of SMART-like steps, though most of them did not fulfill all the SMART criteria, such as identifying who would do them and when:

@@

\item Find a PI (we suggest Neil Chue Hong)

\item Apply for initial funding. For the US, we discussed the Arnold Foundation Open Science award as a planning activity (who, due Dec 15), though without a PI, this seems unlikely to be done.
For the UK, we didn't have a suggestion.

\item Determine project name, initial vision, initial mission, logo (who, when)

\item Identify initial use cases (who, when)

\item Identify potential stakeholders and partners (who, when)

\item Discuss this idea with potential partners (who, when).
Then hgt their feedback \& buy-in.
While doing so, seek suggestions for the right project manager to coordinate this

\item Build up an advisory board (who, when)

\item Build up a leadership committee and determine a leader (who, when)

\item Hire a project manager (who, when)

\item Iterate use case with stakeholders (who, when),
e.g., funders, Researchfish, researchers, ?

\item Iterate vision \& mission with leadership committee and advisory board (who, when)

\item Develop initial development plan (who, when)

@@

If you are interested in more information, please join the WSSSPE team's Slack channel for this working group: \#wg-open-research-idx.  (See \S\ref{sec:slack} for instructions on how to join the Slack WSSSPE team.)
